---
output: github_document
---

# deltaoutbreak

`deltaoutbreak` is a teaching R package that **reconstructs** the analysis from  
*“COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2”* (PMC8993115).

Because the original article did **not** publish row-level data, this package uses a **synthetic dataset** generated in `data-raw/delta_cases.R`.  
The dataset keeps the key signal from the paper: **the Delta period put more pressure on border quarantine systems**.

## Installation

You can install the development version from GitHub with:
```{r}
# install.packages("remotes")
remotes::install_github("Jiner-H/deltaoutbreak")
```

## Shiny app
This package ships with an interactive Shiny app to explore pre-Delta vs Delta periods.
```{r}
library(deltaoutbreak)
run_delta_app()
```
The app:
uses the package data (not read.csv)
lets you filter by period
shows time series and a period-level summary
explains how to interpret the outputs

## Data
The main dataset is:
```{r}
data("delta_cases")
head(delta_cases)
```
It contains monthly observations from 2020-11 to 2021-10, with:
period (pre-delta / delta)
arrivals
detected_in_quarantine
leakage
local_cases
rate variables for plotting

## Functions

Key helper functions:
filter_period() — filter the dataset to one period
summarise_leakage() — period-level summary (used in the Shiny app)
plot_leakage_trend() — quick ggplot for vignettes / reports

## Documentation website

The pkgdown site for this package is here:
https://Jiner-H.github.io/deltaoutbreak/

## Notes
Data are synthetic.
Structure and variables are aligned with the analysis described in PMC8993115.

