---
title: "Exploring quarantine performance during the Delta period"
author: "Jin Hu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring quarantine performance during the Delta period}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(deltaoutbreak)
library(dplyr)
library(ggplot2)
```

### Background

This package reconstructs a synthetic dataset based on the article:

> **"COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2" (PMC8993115)**

The original article did not publish row-level data. We therefore simulated monthly observations representing arrivals, detected infections in quarantine, leakage events, and resulting local cases. The aim is to provide a *teaching dataset* that still shows the key pattern from the paper: **the Delta period placed greater pressure on border quarantine systems.**

### Load the data

```{r}
data("delta_cases")
dplyr::glimpse(delta_cases)
```

### Summaries by period

We can use the helper function that ships with the package:

```{r}
summarise_leakage(delta_cases)
```

This table should show that the delta period has higher detected infections and more leakage on average.

### Plotting leakage over time
```{r}
plot_leakage_trend(delta_cases)
```
This plot illustrates how leakage events changed around mid-2021, when we switch from pre-delta to delta.


### Reproducibility
The data were generated using the script in data-raw/delta_cases.R. You can re-run that script to regenerate the dataset if needed.





















